\noindent
Fuck the people that say life is a cycle of ups and downs. \\
All there is boredom and bullshit. \\
Any and all happiness is a poor facade.  At least, it is for me\ldots


\dayheader{Dawn of the First Day}


\noindent
Same bat-cave.
\\
Same bat-time.
\VV


\noindent
Like usual, \april{} was talking about something trivial.
\VV


\noindent
Talk, talk, talk,
\\
Is that all women do?
Sometimes I regret this cycle I've fallen into.
\\
Work.  Coffee.  Work. Everyday. \textit{No} exceptions.
What are weekends for again?  Oh, right, more work.
\VV

"\ldots{}and \eric{} just wouldn't stop taking shots.  So I left him there."
\VV


\noindent
I wasn't paying much attention before that.
\eric{} was just an alcoholic asshole.  It's always the same story.
\VV


"That's horrible, \april.  He really should have stopped when you asked.
Especially after those DUIs." \textit{Of which he's had three.}
\VV


\noindent
I hate auto-pilot conversations.
But I'm a nice guy and I wouldn't want to be rude.
So I let her continue.
\VV


"I know! And that's not even the worst of it!
His friend, Jake, brought him back past midnight and woke me up.
They were covered in mud!  It was all over the carpets, \josh!
I had to help him into the bathroom where he threw up everywhere.
I was so angry, \josh.  So angry.  I yelled at him a little."
\VV


\noindent
\april's expression showed sliver of guilt.
She's extremely easy to read and I like that.
It's nice when people are more predictable.
When she feels guilty she often raises her eyebrows, just so, showing off
those lovely green eyes.  Then she curls her upper lip with a soft bite.
If she's feeling \textit{really} guilty, she will tap the tips of her
index fingers together about waist-high.
No tapping this time.  She must have felt at least somewhat justified.
I was oblidged to agree.
\VV


"I felt really bad\ldots{} he started crying and apologizing and saying that he
was going to lose me if he doesn't stop drinking."
\april{} continued, her voice becoming more and more child-like.
Another of her \textit{habbits}.
\VV


"I don't know what to do, \josh."
\VV


\noindent
I sighed.  There's always something stupid going on.
%\textit{Oh}, some 18 year old was accused of rape by some
%16 year old girl who got way too drunk and decided the
%next morning that she had made a mistake?
%The fuck do I care what happens to an unlucky boy and
%a stupid cunt?
\VV


"You shouldn't worry, \april.  It was his fault.
He needs to stop drinking so much." I said on cue.
\VV


"Maybe\ldots{}" She said, conceding slightly,
"Sorry if I'm talking too much.  You probably have to go back to work."
\VV


\noindent
\april{} started fidgiting.  Great.  Was she nervous?  Expectant?
I don't friggen know.  Regardless, she does this too often.
\VV


"Never apologize to me for speaking.  How many times must I say it?
We are friends because I find what comes out of your mouth--
that raw manifestation of self that is so utterly, undeniably you--
to be interesting.
I adore conversing with you and hearing what you have to say.
There's no need to apologize."
I replied, managing to spare a brief smile.
\VV


\noindent
She blushed slightly and thanked me with a soft "awww".  Annoying.
\VV


\noindent
She made some comment to the effect of
"We're friends because I wanted us to be.  Not you."
\VV


\noindent
Really?  I remember it perfectly.  I don't forget things, not like this.
Roughly two years ago, I walked into the caf\'e expecting the oddly chipper
voice of \emma{} to greet me.  Instead, I found this petite brunette who didn't
look to be older than 20.  She was quiet.  Everyone is at first.
I think it's my face.  It scares people.
Apparently I look like a serial killer.
\textit{Resting Serial Killer-Face}.
Why? I don't know.  I'm quite fond of my face.  Do I need to smile?


Several months had gone by since \april{} had taken over the morning shifts from
Miss \emma.  Slowly I had gotten her to speak, but she was still behaving
shyly.  One day she had asked me about my weekend and so I told her a tale
of a friend's depressing birthday.
\VV


"I would have told all those bitches off if it were mine."
She said as she threw her arms into the air with an obvious tone of annoyance.
\VV


\noindent
It wasn't much, but I couldn't help but grin.  Finally an unexpected response.
She was now more than just some stupid existence.
I wouldn't have quite called her \textit{interesting} at this point,
but I knew she had potential.
\VV


\noindent
She was still very guarded around me which meant I needed to put in some work.
\VV


\noindent
Over the next two months I changed how I spoke to appear more endearing.
Tone and inflection can do a significant amount of work, but those are often
not good enough.  To really create that feeling of trust in another individual
body language is important.


I would ask about her life with a smile.  I hate smiling.  While listening,
I would give a slight tilt of my head to expose my neck.  The neck tilt is
incredibly useful.  It shows that an individual trusts you enough to 
expose themselves to attack. Couple that with raised eyebrows,
one slightly above the other, to show a \textit{genuine} expression of
concern when appropriate and I was on the fast track to my goal.
The expression around the eyes really do the heavy lifting.
If I couldn't nail that then I would have come across fake.


There were times where I thought I was going to fail.  Times when she
closed up.  Times when I thought I'd lose my new toy.
The hand covering the nape of the neck?  Usually a good sign
that a line was crossed and the target is becoming defensive.
Fidgeting often? Also a great tell of nervousness.
But those are just the common ones.


Luckily I didn't make too many poor advances.  By the third month I had her
telling me enough intimate details of her life to build a very good profile.
I build mental profiles for everyone. With enough information
an individual becomes predictable. When they're predictable it's much
easier to show to them that you \textit{care}.


And that's exactly what I did.  I made her believe that I cared about her.
Once that had been established, everything else was just easy.  Easy tends
to mean boring.  I did become bored with her a bit over the last year or so.
I'm maintaining our friendship though, because it may be of use later.
I suppose if I were mean I'd have dropped it already.  But I'm not mean,
just a bit\ldots{}manipulative.  Purely for sport, of course.
\VV


\noindent
I turned and left for work where I did nothing but work.
It's all very technical really, working, you have to do
things that you don't want to do and talk to people you
just want to punch.  There's a certain tact that's
required to not punch someone in the face.
I swear, when someone even gets close to a slide deck
their IQ drops significantly.


Have you ever listened to someone try to spruce up
a boring talk with stale jokes that just cause
moronically long pauses that slow the presentation
down?  It's like a slow death only you don't die at
the end.  You just revive so that you can experience
it all over again in a few minutes, then a few hours,
the next day, \large{}weeks, \Large{}months, \LARGE{}years!\normalsize
\VV


\textit{For this is hell, nor am I out of it.}

