% It has a certain, I don't know,
% ich wei{\ss} es nicht,
% jag vent inte,
% nie wiem,
% no lo s{\'e},
% \large\textit{je ne sais quoi}\normalsize
%\noindent
%Hmm\ldots{} This door is unlocked?  Am I late?  No\ldots{} it's seven o'clock.
%\VV
%
\noindent
The scenery in the caf\'e was as normal as could be.
It's so nice when everything is consistent.
The worn floor beneath my feet winked at me where the ceiling leaked.
The stairs, leading up to the second floor, were still faded and the name,
Caf\'e Breleir, could still barely be made out on the first step despite
the blacks being much less black than they should and the browns all
starting to look the same. The roaster was chugging along
in the corner by the door with a horrible groan and an utter refusal to die.
The wooden frame fencing the monstrosity in was as ugly as always.
Shoddy workmanship never fails to make me cringe.
It's far too easy to measure and align wood for a simple structure.


\april{} was working again.  No surprises there.
Her schedule is remarkably consistent in comparison to the other baristas.
Maybe it's because she's a ``manager''.  Though that word doesn't seem to
have quite the same meaning there as in other retail.
For the large majority of the business hours, there is only one barista
on schedule.  They do double up briefly in the hours around shift changes
which coincide with the expected high points: lunch and dinner.


One of the tables was out of place.
I'm disappointed at how long it took me to notice.


One of the small square, two-person tables had been moved.
Normally all the furniture is put back into place.
I could have let it be\ldots{} but then it would have
stayed that way for a while.


The table was light, no trouble to lift.
I carefully set the table down in a more
appropriate--the most appropriate--place:
right where it belongs.
\VV


``What are you doing?'' \april{} asked from behind me.
\VV


\noindent
She had walked over to the edge of the bar after taking the order
of the older man who arrived before me.
\VV


``The table's position was bothering me.''
\VV


``Okay \josh.'' she said, laughing slightly before returning to
the espresso machine to make the man's drinks.
\VV


\noindent
The man is always there\ldots{} What's his name? Name\ldots{} \dameon!
His name is \dameon. I swear he comes in two or more times a day.
Always ordering the same thing.
\VV


``Two medium vanilla lattes!'' \april{} called from the end of the bar.
\VV


\noindent
\dameon{} was waiting patiently to grab \april's attention
as I approached the front counter.
She forgot to double-cup one of the lattes.
One of them is \textit{always} double-cupped.
\VV


\noindent
Realizing her mistake, \april{} apologized while sliding another cup
under one of the drinks.
\VV


``Thanks \april'', said \dameon{}.
He took the drinks, walking up the stairs to, no doubt, the single table
in the far corner.  It's a good spot. It has the most comfortable chairs.
\VV


``What do you want?'', \april{} said with a rebellious air.
\VV


\noindent
She knew what I wanted. I wasn't about to give in.
Remaining silent, I continued looking at her with a smile.
I knew I'd win.
\VV


``Grr! A coffee? Fine.''
\VV


\noindent
While handing her my card, I switched to a grin.
\VV


``Gah,'' she said softly, returning my card,
``\josh, I don't want to be here!''


``Oh \april. As pleasant as always.''  I said while sighing.
\VV


\noindent
I don't think a day goes by where she doesn't say something similar.
Every time, she gives me this odd look look with a left-tilted head
and a weak smile.  Then she drops her shoulders, rolling her back.
Sometimes she places her hands on the counter and stretches out her spine.
Sometimes she squats down, trying to hide.
This time she just straightened back up.
\VV


``\jasmine{} is being a butt\ldots''
\VV


\noindent
Looks like another good rant for my coffee.
\VV


``So, I had to take a box of chips from the other store
because we're almost out here.  She keeps asking for them back
but I know they don't sell enough sandwiches for that.
I even went and checked the stock, but she keeps insisting!
And then she's was mad because of overtime\ldots{}
Wait, I told you about the overtime, right?''
\VV


``\jasmine{} was angry about overtime?'', I asked, raising an eyebrow.
\VV


``Oh, I thought I told you.
Yeah. She's the one that goes and picks up our checks from the banks
and she saw mine.  By state law, employers' don't even have to
give overtime pay.  But \mike{} actually pays us time-and-a-half if
we work over 88 hours in the pay period.
Like, up to 88 is just normal pay.
Well, last paycheck she had worked 86.5 hours and apparently felt like
she deserved overtime.  She asked me last week when we were working together
if I received overtime.  So I told her I did.  I wasn't going to lie.
I worked 113 hours last week, \josh.''
She said, stopping to take a small, yet audible, breath.
``She got an attitude and asked why and I told her that you only get overtime
for hours over 88.''
\VV


\noindent
I gave some bullshit responses:
``She really shouldn't have looked at those paychecks'',
``\jasmine{} should know the rule''", etc.
\april{} wasn't quite finish though.
\VV


``And then yesterday I had to go to the store because of those chips, 
but the van wont start and \mike{} wont fix it because he only
ever comes back in town for the night to check up on things.
He told me to go do it, but I don't have time.  So I just took
my car which only holds maybe half of what I need to get in a trip.''
\VV

\noindent
She stopped again for a breath.  This time slowly in, slowly out.
She relaxed her eyes as she did.
\VV


\noindent
``It's okay. Everything is okay.'' she said.  ``This is how adults do things.
They manage their stress, right?''
\VV


``You're such a good adult, \april.''  I smiled.
``I've seen you get through worse, you'll be fine.''
\VV


\noindent
She gave me one of those adorable pouts again.  I ignored it.
She needed to be teased.
\VV


\noindent
Eventually she asked what I've been up to, apologizing first of course.
I swear some people are just naturally and disgustingly apologetic.
\VV


``I had a weird dream,'' I explained, ``would you like to hear it?''
\VV


``Yeah!'' she exclaimed with a child's enthusiasm for adventure.
\vspace*{3ex}


\begin{adjustwidth}{2em}{2em}
\noindent\Huge``\normalsize
\begin{adjustwidth}{1em}{1em}
\input{dreams/dark}
\end{adjustwidth}
%\raggedleft\Huge''\normalsize
\end{adjustwidth}
\VV


\noindent
She told me it was a terrifying dream and then recounted one of
her nightmares.  Someone would break into her apartment while she
was sleeping and attack her.  There were some oddities like
the assailant walking on hands and knees and Eric being around
but just sleeping through everything.  As far as dreams go,
it was fairly normal.
