% Third Day -------------------------------------------------------------------
\noindent
I didn't know what to do with my morning.  \april{} wasn't working today.


There was this other brunette working.
She was short and wearing a light gray, deep-collared cardigan\footnote{
  I should get a cardigan.
  Something with nice thick nits and large black buttons.
  Every time I go shopping all I find are thin cotton ones with zippers.
  I don't want to look like Mr. Rogers.
  This isn't story time in the Neighborhood of Make-Believe.
} over a black shirt.
It was a weird choice of color for working at a caf\'e.
I hope she didn't stain it.


I've seen her in here before.
I had assigned her the nickname ``Bubbles'' because she laughs at everything.
I've never bothered to learn her name.  She bores me.


Since I didn't have \april{} around to make me special coffee\footnote{
I honestly have no clue what I normally drink.
\april{} just works her coffee magic.
}, so I just ordered it black and went on my way.
\VV


\noindent
I left work early to take a nap.
I was taking \april{} to the symphony later.
It would have been bad if that headache remained.
It's funny how fucked up a night without sleep can make you.


My head was throbbing continually.
I couldn't think.
It was like my mind was a colloid.
A cloud suspended in my brain.

\lhoarnob
% Third Night -----------------------------------------------------------------
\noindent
I picked up \april{} from the coffee shop since she had to take inventory.
Her outfit screamed secretary:  a tasteful black blouse;
heathered gray pants, untappered; black heels with pointed caps.
I was delighted to find that she had opted for real pants this time,
though a bit disappointed that she wasn't wearing a dress.
At least we matched.


Originally I was going to try and pull off a look that I call
``The Pumpkin Spice Latte''.
It's a very technical outfit.
The ``Pumpkin Spice'' base is a creme chambray shirt with an apricot wool tie
held warmly in place by a ginger, or possibly amber, knit sweater.
The spice is wrapped up nicely in a fitted tweed suit with a knit pocket
square, color-matched to the sweater.
The shoes are the most crucial part.
Black shoes cause too much contrast on the lower body with the beautiful
layering exposed between the jacket's lapels.
Instead this ensemble needs well colored pair of brown Oxfords with
a clean cap toe,none of that wing-tip bullshit.
Nothing too dark as it might blend in with the tweed.
Nothing too light as the color may draw attention away from
the upper body.
The fit needs a good middle-ground.
Something in a nice bronze might do.


Sadly my tie was more of a carrot than an apricot and that just wouldn't do.
I was forced to go with my alternate, ``The Oxford Professor''.
A navy jacket worn over a burgundy argyle sweater, white chambray, and
navy tie.
The pants were heathered gray, though a shade lighter than \april's,
finished off with a pair of untipped black Oxfords.
A pocket square would have made this outfit too formal,
so I left the blazer bare.
\VV


``Hey,'' she said softly, ``you look snazzy.''
\VV

\noindent
%It was an awkward sounding ``hey''.
``Hey'' can be said with a million varied tones, but,
for some reason, her's always sound so \textit{off} when
she greets me outside of work.
\VV


``And you look like you're ready for business.''


``Yeah, when \casey{} saw me she said I looked
like I'm either going to an interview or on a date.
I hadn't told her about orchestra.''
\VV


\noindent
We both laughed.  It really wasn't a date.
She really wanted to go but \eric{} doesn't like
the symphony.  I offered to taker her instead.
I love any chance to dress up.


After small talk was out of the way,
I drove us to the concert hall.
We didn't talk the entire time.
\VV


\noindent
We arrived a little late, but still with enough time to grab a drink
from the bar before finding our seats.


The orchestra was already seated, waiting for the maestro.
The concert was Halloween themed for October and every musician
was in costume.
None of them really stood out.
There was a pharaoh on French Horn and the pope had a tuba.
\VV


\noindent
A recording was played on the speakers of an over dramatized voice
welcoming us to the show.
It reminded me of the intermissions of the old Fright Night marathons
that my father and I used to watch together.


The voice cut out and the conductor walked on stage.
He bowed, the collar of his Dracula costume flopping to one side.


It had been a long time since I'd heard such scores.
The selection was largely from the films of Hitchcock with an
occasional piece from \textit{Fantasia} or \textit{Peer Gynt}.
\VV


\noindent
I think I was happy.
\VV


\noindent
Then the intermission came and \april{} had to open her mouth.
She told me she was breaking up with \eric{}.
I was elated to hear those words.
\eric{} was never good enough for \april{}.
Too often I had to comfort her after an argument.
Too long have I urged her to sit him down and discuss their relationship.
I was hoping they could at least resolve their issues,
but after the recent spike of alcohol related stupidity,
a break up is much more appropriate.


She went on though.  She couldn't leave it at that.
\VV


``I'm in love with someone else,'' she said,
``Do you remember \crosby?''
\VV


\noindent
Of course I remember fucking \crosby!
It was obvious that she was attracted to him.
Hell, the guy even told her that he liked her, but
he was married.
\april{} asked him to come talk to her if they ever divorced.
I didn't see \textit{that} coming.
\VV


``He's taking me to the mountains in the middle of November for a vacation.
He told me I work too much.
I've already been out with him a couple of times.
Does that make me a bad person?
Going out while I'm still living with \eric\ldots''
\VV


\noindent
I had to think over my response and try not to cringe.
She developed commitment issues after \blake{} had cheated on her.
And then this?  This isn't suppose to happen.
This is too fast.  Too \textit{unpredictable}.


I responded with some shit about how it's normal and that it's okay
but I would have preferred if she had broken it off with \eric{} first.
\VV


``Opportunities don't often wait.
Just try not to do it again.
You remember what \blake{} did to you.''
\VV


\noindent
I would have liked to have just ended it there.
I really didn't have enough alcohol for this.
She just constantly bombards me with these trite matters
like rocks beneath a waterfall of words.
\VV


``I think he loves me.''
\VV


\noindent
Great.
\VV


``But I don't think I'm good enough for him.''
Her voice became smaller.
Even puppies learn from their mistakes, but her?
I think she just likes my lecturing.


``Look, \april{},'' I began,
``No one is too good for you.''


``But he's really successful and
I look at my life and I'm just a barista.
I haven't gone anywhere at 30.''
\VV


\noindent
How many times can I sigh in one conversation before it becomes obscene?
\VV

``First, you aren't 30 yet. You're 29.
Second, If I thought you weren't going anywhere in life,
do you really think I'd be your friend?
Do you really think we'd be sitting here right now?''
\VV


\noindent
I wasn't exactly convinced of that,
but it didn't matter if \textit{I} was convinced.
Only that I was convinc\textit{ing}.
\VV


``You're right\ldots{}''  She didn't sound too sure.


``You know you can trust me.''
\VV


\noindent
She shook her head in acknowledgment.
I guess she had to think through the worry.
\VV


\noindent
The remainder of the symphony was just as spectacular
as the first half.
I was almost sad that we had to leave.
\VV


\noindent
I dropped her back off at her car.
We didn't speak again in the car.
She just had this worried look on her face
the whole time.
Parallel eyebrows, scrunching her nose.
She was rolling the right half of her bottom
lip gently between her teeth.
This caused the left half to poof out just a bit.
It's no use trying when she's like this.
She'll work it out.
She's an adult despite how childish she acts.


She thanked me for taking her to the orchestra around five times as
she was exiting the car.  I swear she tries too hard.
I told her once was enough.  I got a small smile out of that.


I wished her goodnight and set off for home.
\lhoarb
