
\noindent
Once upon a lime in the Sour Green Valley, \uglyF{}, fast asleep, dreamed of a day
where he were shaped like a potato instead of a yam.  But the sweet, potato dreams
would not last.  \ugly{} awoke with a frown, disappointed by his white, starchy body.
\VV


\noindent
His disappointment didn't last long------

\noindent
A distinctive knock echoed through the house\ldots{}
\VV


\textit{Knock-a-lock-lock-lock-knock-a-lock-lock}


\textit{Knick-Knock Ka-knock-a-lock KA-\large{}PLOCK\normalsize}
\VV


\noindent
\ugly{} jumped\footnote{
Jumping is a bit misleading when referring to a creature as magnificent as \ugly{}.
The movement was closer to a that of a boastfully large ship sinking into the depths after an unfortunate
run-in with a glacier that had a nasty case of the Mondays and an adamant refusal to move.
}
to his hooves, sending ripples across his girth that temporarily consumed his tiny legs.
% This should be the footnote break (eh...)
\ugly{} knew this knock.  There's only one knocker with a knock so knockticular this side of Knockington Central.
\uglyF{} unlocked the door and \yoloF{} forced his way in.
\VV


"Yodl-do \ugly{}", \yolo{} said, "how're you?"
\vv

"Hey, \yolo{}", said \ugly{}, sheepishly, "I'm well.  What brings you here?"
\vv

"Just felt like checking on you."
\vv

"Oh, no one ever checks on me...",
said \ugly{} in a tone flat enough to bore a child to sleep.
\VV


\noindent
\yolo{} ignored this.
\VV


"Hey, what do you say we yodle on down to the park and see what good ol' \pixel{} is up to?"
\VV


\noindent
\pixelF{} was always up to something.
She once licked herself, and twenty-seven other animals, raw to beat the world record for largest
regurgitated hair ball.  She broke the record and dilapidated half of the village.
\VV


\noindent
Currently, \pixel{} was staring attentively at a mismatched flock of birds and
softly singing to herself\footnote{
\pixel{} is strongly under the mindset that singing, like nap time, is a necessity
in life. Why, you can sing about anything: gardening, baking cookies, setting
up an elaborate Rube Goldberg machine to catch that pesky mouse who has alluded you
for so long.  Yes, singing keeps the mind sharp\ldots{} but not as sharp as \pixel's
claws.
}.
\VV


\doublenewpage
\noindent
\pixel's song went a bit like this:
\VV


\textit{A goose, I spy, Greylag? Andean!}


\textit{A dove, I see, Topknot? Mourn-ING!}
\VV


\textit{I wonder--wonder--how they are--}


\textit{Like Gull? Perhaps Vanga?}
\VV

\textit{Another here\ldots{} a pigeon too!}


\textit{How I'd like a taste of you!}
\VV


\textit{I'll count to three and then I'll spring!}


\textit{And with my claws I'll try to cling}


\textit{Onto your juicy winged boooooooooodieess!}
\VV


\noindent
No sooner had \pixel's song ended did she leap into the air toward the flock.
The birds scattered.
\VV


\noindent
This was of no consequence to \pixel.  She, like many animals, loved a good chase.
And this chase was looking to be exemplary.
\VV


\noindent
Then \gooseF{} waddled into the nearby lake hoping the water would be safe
from the cat.  Little did \goose{} know, \pixel{}, unlike most domestic feline folk,
loved the water.  How could she not?  It was like bath time with larger,
more feathered, less rubbered ducks.
\VV


% Pixel slunk <break: "Wait slunk?"
% "yes, slunk."
% "haha, \quaid, no one uses words like that."
% "Well, I do, anyway, Pixel MOVED..."
\noindent
\pixel{} slunk to the edge of the water on which the unsuspecting \goose{} sat.
She dipped a paw in, slowly, sending a small rippled no more prominent than
the fall of a leaf across the surface.  In moments, \pixel{} was in.
She waded out a bit before submerging herself.
\VV


\textit{\Large{}Glub\normalsize---\Large{}glub\normalsize}


\hspace*{14ex}\textit{\large{}Glub\normalsize---glub}


\hspace*{25.5ex}\textit{\large{}Glub\normalsize--glub}


\hspace*{36ex}\textit{Glub--glub}
\hspace{1ex}\textit{glub--glub}
\hspace{1ex}\textit{\large{}glub\normalsize--\LARGE{}Glub\normalsize}
\VV


\noindent
\pixel{} leapt from the water and latched onto the goose!
\goose{} flapped violently in an attempt to stay afloat with her new found
cat-skin-and-entire-body coat\footnote{
A live cat is a hard look to pull off.  \peacockF{} once fashioned
one for her \textit{Catmares} collection last winter.  It was a sight to behold.
The darling Miss \peacock, in all her radiance, boldly strutting the runway
with a tom cat clinging for it's life on her back.  The colors of her tail feathers
perfectly contrasting with the mangy gray fur of the cat.  It was a wonder if
such extreme fashion would ever see the light of day again.
Though, today, while clearly a knock-off, the onlookers of the struggle between
\goose{} and \pixel{} could only be reminded of the brilliance of \peacock's design.
}.

%Other two birds need to distract Pixel
%Then yolo and ugly show up
