The dream opened at a university that was not unlike the campus at the UA.  There was a decently nice landscape, lots of grass and dorms that all looked the same:  Giant rectangular buildings of no particularly unique quality.  There was a sort of activity going on outside in the center of the campus.  Just about every student was there.  At the end of the event--or whatever it was--I saw Maria walking away ahead of me. (I didn't really have a reason for doing this, I just... I just wanted to.) I quickened my pace to catch up with her.

  "Hey, Maria..." I called.
She turned and looked at me, "hey...?"
  "I was wondering if you'd like to get dinner with me sometime."
It was a rather dumb line, but I said it regardless.  Her composure as well as her expression never changed as she uttered a rather solemn "No, I don't think I can."
Anyway, we both just starting walking our seperate ways.

It kept haunting me, what she said and how she said it.  Now, I have no problem with being rejected, but it was as if she knew what I was going to say before I'd said it.  How could she know my intention if I did it spontaniously?  I really wanted the chance to find out, but unfortunantly that seemed unlikely.

Later that evening after I'd made my peace with the rejection, I began exploring the building that I found myself in.  It was and was not like the other dorms.  It was indeed a dorm, same old rectangular building, but it had the odd capacity of also being partially church like.  As I was walking through what appeared to be a chapel, I saw a priest being rather suspicious.  I decided to follow him.  He went up a flight of stairs and into an unused room.  I waited until he had left to explore.  The room was covered in cobwebs and various oddities.  What I found was rather shocking:  Plans by one of the other students to kill Maria.  I didn't know why or how the priest was involved, but I did know that I needed to stop it from happening.

Now, Maria was more than protected.  Her and a few other students possessed certain unusual weaponry:  Claws.  These claws were similar to those of Freddie Crugger's.  They just looked a whole lot better.  They were blue and seemed to be made of fiberglass framing with retractable steel blades at the ends of each finger.

So, I went off to find this person.  I ended up finding him outside a fairly close by dorm harassing Maria.  I didn't know the reasoning for it, but I ran at the guy and knocked him to the ground. She ran off and when I turned back to him, he was running off in a different direction.  I then decided to get myself a pair of the claws.

That evening I re-found and followed the guy to the university's food court.  The food court was packed and there was little to choose from in terms of seating.  Nevertheless he found and sat by Maria, smiling his evil little smile.  I went in as well, forcing the person beside him out and sitting down.  Everyone was sort of looking at me then.  He tried to get up and leave.  I stood up, kneed him in the crotch and threw him to the floor.  I continually beat him once he was down.  After he stopped moving I retook my seat.  Everyone beside Maria had left by now.

  "Well, how about that dinner, then?" I said.
Her expression didn't change once again as she said, "I don't think it'll work out."  I wasn't going to take that as I'd just saved her.  After some more talking about it, she finally asked me "What sort of music do you listen to?" in an attempt to prove that it wouldn't work out.
  "Metal and Classic Rock," I replied.
She laughed.
  "Alright, then," I said, "I know you're going to some concert soon, why don't I just join you and see what's so great about your music."
She didn't really have anything against this and agreed.  At the concert I realized it was just a genre of rock not that bad.  I wondered why she'd laughed earlier, but I ignored the thought and just wanted to enjoy my victory.

