%\dayheader{I, Apocolyptic}
``Just a taste,'' the witch said urging me to drink from an ornate hourglass.
\VV


\noindent
The hourglass was bound in silver on both ends with two silver dowels adding support to
the fragile glass structure.  Carved into the housing were little figures of men--
some with horns, others with wings.  There was a tiny hing and a latch on top.
Held in the glass was a mound of red sand pilling up slowly.


I didn't bother asking why.  I popped open the latch and knocked it back like a shot.
Unfortunately the tapering kept the stream slow and steady.
It reminded me of a cherry Pixie Stick.
I choked for a bit, being suffocated by the granules.
I could see the witch smiling as I passed out.


I opened my eyes to pure darkness, save for a flickering light bobbling
towards where I lay.


A creature with decaying skin and ebony eyes was staring at me from behind the light.
It was crouching.  The more I looked, the more it stared.  Hypnotized by it's abyssal
eyes gleaming in the light, I saw that it--he--was me.
A different me, but undeniably so.
\VV


``Welcome to the darkness.''  The other me hissed.
\VV


The gray-skinned me hobbled off down some passage, invisible in the dark.
I tried to stand, but quickly found the ceiling too short.  Crouching as well,
I followed the light into the unknown.


The passage was musty and smelled of fungus.  There were no seams nor mortar in
the walls from what I felt.  Just solid concrete.


The light flickered out and the scraping of the creature's nails stopped.
I kept moving.  What laid before me I did not know.
What laid behind me was likely no better.


The walls stayed solid, but soon, my feet found a ledge, and my mind too late.
I slid off the edge, my fingers bloodying as I tried to grip the concrete.

I woke as soon as I began to fall.
%
% Should this be in poem form?  French?
%
