%\dayheader{Vermilion Skys}
\noindent
I was standing in a park reminiscent of
Georges Seurat's ``A Sunday Afternoon on the Island of La Grande Jatte''.
% Describe the people plox.
There were countless people looking out onto a crystal clear pond.
I was absorbed into the tranquility of the park,
relaxing in the shade of a nearby tree.


The sky turned dark and the world was suddenly stained, monochromatic, with red.
A dozen hooded figures stormed the park, killing everyone in sight.
I ran, avoiding the fallen bodies.
There wasn't anywhere to go except to the water.
I thought I might be able to hide under the surface, or at least reach
the opposite shore.


I stopped just short of the lake's edge and gazed out over the bloody water.
The surface bubbled, molten.
A great black spire erupted from the water.
The imposing figure of the tower seemed to look down on the world--
to look down on me.
I dropped to my knees.
I could hear footsteps in a slow stride echoing in the hollow air.
\VV


``You can never run from me.''
\VV


\noindent
The voice was taunting and familiar.
There was a click and I was dead.
\VV


\noindent
With my conscious free from my body, I saw that the killer was me.
I drifted into his head.  From his--my--eyes I saw a cop lying on the ground.
He was bleeding out but still moving.  He pulled his arms out in front of his
prone body.  He was holding a pistol.  Shaking violently, he shot.
The bullet penetrated my heart.  I could feel the force tearing my flesh.
\VV


\noindent
Again, I was dead.

