%\dayheader{The Desolation of Alice}
% Rewrite this shit
% Alice -> Avril
% Where does Quaid come in?
% Maybe leave Quaid out of this.
% Use as a forshadowing of Avril being killed (evilness)
\noindent
Far removed from civilization, there existed a mansion.
The mansion was lavish; luxurious far beyond what would reasonably be considered ``rich'' by the largely poor population of the towns surrounding the forest.
No one had ever seen the mansion, but it seemed to become increasingly more like a castle with each recitation of the rumors.
There were---supposedly---large, beautifully carved wooden doors and stained glass mosaics of the god of death and corruption, Deimos.


In this rumored mansion, there was a woman leaning against the second floor balcony of the entrance hall.
She had blonde hair and wore an elegant, soft violet night gown.


Through the apparent peacefulness of the night, a knocking came at the front door.
The woman, alarmed that someone would actually know where to find her, just kept staring at the door in fear.
The knocking came again.  After a few minutes int the silence after, the doors burst open.


In stepped a large creature with eight thick spider-like legs with a mans torso and fairly bulky arms---one of which, had what can only be described as a claw, growing from it.
The head of the creature was human-shaped, though it mostly resembled an ogre's.
Behind it stood a slightly smaller version of the same creature.


The larger of the two spoke in a loud, growling voice.
\VV


``This is now, and forever will be, my domain.''
\VV


\noindent
The girl panicked, and did what any self-respecting female in a horror movie would do: she ran.
She ran toward the mosaic of Deimos overlooking the lake behind the building.
With only one way out in sight, she hurled the doilied hall table into the glass, shattering it.
Quickly jumping off into the lake below, she heard the \textit{thing} calling behind her:
\VV


``You can't run forever.''
\VV


\noindent
Dragging herself out of the water, she cautiously entered the forest.
After a few hours, she had exhausted the adrenaline that kept her running and decided to rest for a moment or two.
Just as she had taken a seat, she heard a rustling in the near by overgrowth.
An old man wearing a dark cloak approached.
\VV


``Where have you come from, my dear?''
\VV


\noindent
The girl said nothing.
\VV


``The mansion, eh?'' he said, ``Then you must be Alice!''


``H-how do you know of me?''
\VV


\noindent
The hermit ignored the question.
\VV


``I take it they found you? Well we better get going, then.''


``They?''

% Change name...
``Octorots, we call them, ugly things.'' the man said,
pushing aside some nearby bushes to reveal a tunnel. ``Now come along.''


``Wait, where did they come from?''
\VV

\noindent
He sighed.
\VV


``Some time ago a group of those hapless void wizards attempted to raise the black bishop of Hell, when they were refused ice cream with their apple pie. The stupid fools managed to screw up the ritual, and instead of raising the Bishop, they got a portal to the wrong layer of Hell trapped open.''


``Is there anything we can do, to stop the Octorots?''


``Well... you'd better come down into my cave.''
\VV

\noindent
Alice followed the man down the hole.
Once inside, the man walked over to a small table that supported a single object.
A staff of archaic design with a large multi-colored jewel sitting atop.
\VV


``This is the staff of Helios,'' he said, picking up the staff, ``It's an ancient tool that can only be controlled by a few gifted students of the Nexus.''
\VV


\noindent
He presented it to her.
Alice reproachfully touched the staff. The jewel began to shine in a rainbow of brilliance.
\VV

The hermit's eyes flashed as he said ``Helios seems to smile upon you.''


``Can this staff stop them?''


``It's quite possible.''


``How do I use it?''


``Engraved on the staff are the words: \textit{a' tuulo' i' mor-cevan, arphen od fatanyu}. I'd suggest you say them when faced with the beasts.''
% (pronunciation: ay tee-yew-lu e more say-van arf-in odd fate-an-you)
\VV

% Stuff here?

\noindent
Alice approached the mansion.  The small octorot stepped out from the wreckage of the doors.
\VV


``Hehehe, we've been waiting for you.'' taunted the little shit.
\VV


\noindent
The small octorot let her inside.
The large octorot was sitting on the balcony... the entire balcony.
\VV


``I see you've decided to return.'' Scoffed the larger of the two.
\VV


\noindent
Alice pointed the staff of Helios and began chanting the Elvin words.
A majestic display of color and energy shot from the staff.
The big Octorot laughed and stepped forward.
\VV


``You think \textbf{me} can stop \textbf{me}?''
\VV


\noindent
He took a swing at her with his clawed arm.
Alice fell to the ground.
The old man stepped into the room, smiling.
He took a knife from under his cloak and stabbed Alice's limp body through the heart.
\VV


``\textit{O sereg ettul a ingole' o tofn ist. Eria mor-pen!}''
% (pronunciation: oh sare-egg ett-ule ah ing-olly oh toff-in ist. err-eye-a more-pen)
\VV


\noindent
The blood flowing from her body began to fill an intricate engraving on the floor.
Once filled, the markings on the floor began to shine and a black mist rose around her body.
A figure with a head full of needles rose from the mist.
\VV


\textsc{Am I too late for the party?} Came a lifeless voice from the doorway.


``A voice so monotonic that it could \textit{kill}... So nice of you to join us Death.'',
said the old man laughing.
\VV


\noindent
Death ignored the man and walked over to Alice's body that the bishop was currently feasting upon.
\VV


\textsc{If you would excuse me, I need just a moment.} said Death, taking out his scythe.
\VV


\noindent
Alice's soul rose from her body and stood in front of Death.
\VV


\textsc{It's time to go, Alice.}
\VV


\noindent
With one swift movement, the scythe ripped through Alice's soul, causing it to disappear.
Death turned to leave.
\VV


``You aren't going to stop me?'' asked the man.


\textsc{I need to go feed Snickers.}


``Hunger...'', the Bishop muttered as it approached the old man's body.
\VV


\noindent
The Bishop gripped his jaw and pulled it down until his mouth spanned the entire height of the hermit.
\VV


``Destruction...'', The Bishop muttered as it walked into the forest,
setting the foliage ablaze with every step.
