The dream opened in my room, chatting on irc.  Me and you were just talking and for some reason I decided to go visit you in Sweden... Also, it seemed the method to get to Sweden only involved me leaving my house.  So I was in Sweden and it was fairly derelict.  there was an area of sand with a destroyed building in it that transitioned to patches of grass.  To get to your house, my directions were something along the lines of: take a NE direction once you get to a notch in the destroyed building; keep walking up and over the hill ahead into a valley; the house is a darkish purple on a sort of scale-shingled texture--The trimming was yellow, I think. It was a cute house, but a bit unreal.

There was no knocking or ringing of a doorbell, I just opened the door and entered the main room; the room was located directly after the door. There was a television to the left and assorted furniture to the right.  You were sitting on a yellow-gold chair. You had dirty-blond, straight hair and were wearing dark clothing (my description of the clothes is a bit pointless, so, I omitted it)

I uttered, "Hello..."
"You seem different than I expected you would," you returned.
"Same to you..."

We sat in awkward silence for the next period of time--no recognition of the passage of time in my dream. I just got up and left, then I woke up.

I soon slipped back into sleep with the same dream setup.  This time, however, when I said I would be going to Sweden, there was an agreement that I'd stay the night--although Sweden seemed just outside the door, the border was assumed to still be over sea. When that was agreed upon, you said, "This will be a first, for you."--an odd statement. Me and my dad set out--my dad was with me to see where i was going to be; probably fragmented from my knowledge of his protective nature. When we got to the destroyed building, I couldn't find the notch for awhile; eventually I found it and we went on our way.  There were 2 houses surrounding yours in the valley. My father then disappeared.

 I entered your house but this time there were more people there. A group of people dressed in black, all with assorted guns. One of them was smoking something that looked like a giant cigar surrounded by several smaller cigars. You were still in the same chair to the right.  You looked at me with an almost dead stare, an emotionless face. (your hair was black this time, also)

"Hello, Victoria" I said.  
"Quaid." You said, "After the last visit, sitting in silence, what did you expect to find different?"

I woke up upon that note, about two minutes before my alarm was set to go off.  I fell back to sleep for a third time. You and I were still in the house, but the rest of the people were gone. You held a crossbow pointed at my chest.  The alarm sounded; I awoke for the final time.
